Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2021-01-01 analysis/corpus.Rmd
Add 3.1

---
title: "Corpus Analysis"
output: html_document
params:
  base_dir: ../../../
editor_options: 
  chunk_output_type: console
---

@@

# TODO: move into the package
source("inc/paths.R")
source("inc/setup.R")
source("inc/latextags.R")

options(repos="https://cran.r-project.org")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "corpus.tex"), prefix="Corpus", default=TRUE)
```

@@

```{r load corpus}
evals_dynamic <- read_fst(PACKAGE_EVALS_DYNAMIC_FILE) %>% as_tibble() %>% rename(evals_dyn=n)

corpus <- 
  read_fst(CORPUS_DETAILS_FILE) %>%
  as_tibble() %>%
  left_join(evals_dynamic, by="package") %>%
  mutate_at(
    vars(
      starts_with("runnable_code"),
      starts_with("runnable_files"),
      starts_with("package_"),
      starts_with("funs_"),
      "evals",
      "evals_dyn"
    ), 
    replace_na, 
    0
  )
```

## CRAN packages

```{r filter out inconsistent programs}
corpus_programs <-
  read_fst(CRAN_PROGRAMS_FILE) %>%
  as_tibble()
```

```{r summary}
runnable_code <- 
  corpus_programs %>%
  mutate(files=1) %>%
  pivot_wider(names_from=type, values_from=c(files, code)) %>%
  select(-file, -runtime, -error, -success, -corpus) %>%
  group_by(package) %>%
  summarise_all(sum, na.rm=TRUE) %>%
  group_by(package) %>%
  mutate(
    files=files_examples + files_vignettes,
    code=code_examples + code_vignettes
  ) %>%
  ungroup()

corpus_program_examples <- filter(corpus_programs, type=="examples")
corpus_programs_tests <- filter(corpus_programs, type=="tests")
corpus_programs_vignettes <- filter(corpus_programs, type=="vignettes")

overview_table(
  r("packages",    corpus),
  rs("revdeps", corpus$revdeps),
  r("in cranlogs", filter(corpus, !is.na(rank))),

  rs("package programs",         runnable_code$files),
  rs("package programs code",    runnable_code$code),

  rs("examples programs",  runnable_code$files_examples),
  rs("vignettes programs", runnable_code$files_vignettes),

  rs("examples code",  corpus_program_examples$code),
  rs("vignettes code", corpus_programs_vignettes$code),

  r("mean expr coverage",   percent(mean(corpus$coverage_expr))),
  r("median expr coverage", percent(median(corpus$coverage_expr))),

  r("with R code",      filter(corpus, package_r_code > 0)),
  r("with native code", filter(corpus, package_native_code > 0)),

  rs("code",        corpus$package_code),
  rs("R code",      corpus$package_r_code),
  rs("native code", corpus$package_native_code),

  rs("functions",          corpus$funs_public + corpus$funs_private),
  rs("function with eval", corpus$funs_with_eval),
  rs("public functions",   corpus$funs_public),
  rs("private functions",  corpus$funs_private),

  rs("revdes", corpus$revdeps)
)
```

```{r generals}
overview_table(
  r("all cran", dim(available.packages())[1]),
  r("core packages", length(CORE_PACKAGES)),
  r("most downloaded treshold", MOST_DOWNLOADED),
  r("large package treshold", PACKAGE_SIZE_OUTLIER),
  r("evals package treshold", PACKAGE_EVALS_OUTLIER)
)
```

@@

```{r plot corpus}
coverage_mean   <- mean(corpus$coverage_expr)
coverage_median <- median(corpus$coverage_expr)
revdeps_mean    <- mean(corpus$revdeps)
revdeps_median  <- median(corpus$revdeps)
funs_with_eval_mean    <- mean(corpus$funs_with_eval)
funs_with_eval_median  <- median(corpus$funs_with_eval)

size_bins       <- c(0L, 1e3L, 5e3L, 1e4L, 5e4L, 1e5L)
size_bins_lasb  <- c("< 1000", "1,000 - 4,999", "5,000 - 9,999", "10,000 - 49,999", "> 50,000")

corpus %>%
  mutate(
    outlier=evals_dyn > PACKAGE_EVALS_DYN_OUTLIER,# | package_r_code > PACKAGE_SIZE_OUTLIER,
    label=ifelse(outlier, package, NA),
    code_size=cut(package_r_code, size_bins, labels=size_bins_lasb, include.lowest=TRUE)
  ) %>%
  ggplot(
    aes(
      x=coverage_expr, 
#      y=funs_with_eval,
      y=evals_dyn,
      label=label,
      size=code_size
    )
  ) +
  geom_point(alpha=.4) +
  geom_text(size=3, check_overlap = T, vjust=-1.5, na.rm = TRUE) + 
  geom_hline(aes(yintercept=funs_with_eval_mean), linetype="dashed", color="red", size=0.2) +
  geom_vline(aes(xintercept=coverage_mean), linetype="dashed", color="red", size=0.2) +
  scale_x_continuous(labels = scales::percent) + 
  scale_y_continuous(trans=scales::pseudo_log_trans(), breaks=c(0, 1, 2, 5, 10, 20, 50, 100, 200, 500)) +
  scale_size_discrete(range = c(1, 6)) +
  theme(
    legend.position=c(0.2, 0.85),
    legend.box="horizontal",
    legend.box.background = element_rect(fill="white", size=0.1)
  ) +
  labs(
    x="Code coverage", 
    y="Number of eval call sites", 
    size="Lines of R code",
    linetype=""
  ) +
  guides(
    size=guide_legend(order=1),
    color=FALSE,
    linetype=FALSE
  )

ggsave(CORPUS_PLOT)
```

### List of corpus packages

```{r list of packages, eval=FALSE}
datatable(
  corpus, 
  filter="top", 
  options=list(
    pageLength=50,
    autoWidth=TRUE
  )
)
```

## Kaggle

```{r kaggle dependencies}
kaggle_dependencies <- tibble(package=read_lines(KAGGLE_DEPENDENCIES_FILE))
```

```{r compute kaggle programs}
kaggle <- read_fst(KAGGLE_KERNELS_FILE) %>% as_tibble()
kaggle_programs <-
  read_fst(KAGGLE_PROGRAMS_FILE) %>% as_tibble() %>% filter(success)
```

```{r kaggle summary}
kaggle_code     <- kaggle_programs$code

overview_table(
  r("kaggle",                 kaggle),
  r("duplicated kaggle",      nrow(kaggle)-nrow(filter(kaggle, runnable))),
  r("runnable kaggle",        filter(kaggle, runnable)),
  r("finished kaggle",        kaggle_programs),
  r("failed kaggle",          nrow(filter(kaggle, runnable))-nrow(kaggle_programs)),
  rs("finished kaggle code",  kaggle_code)
)
```

```{r}
setdiff(kaggle_dependencies$package, corpus$package)
```

## Combined

```{r compute programs}
programs <- bind_rows(
  corpus_programs %>% select(code, runtime, corpus),
  kaggle_programs %>% select(code, runtime, corpus)
)
```

```{r all summary}
overview_table(
  r("all programs",      nrow(kaggle_programs) + nrow(corpus_programs)),
  r("all runnbale code", sum(kaggle_code) + sum(runnable_code$code)),
  r("all code",          sum(kaggle_code) + sum(corpus$package_code) + sum(runnable_code$code))
)
```

```{r programs-code, eval=F}
programs %>%
  ggplot(aes(y=code, x=corpus, fill=corpus)) + 
  geom_violin() +
  scale_y_log10(labels = scales::comma) +
  scale_x_discrete(labels=c("kaggle"="Kaggle", "packages"="Packages")) +
  scale_fill_viridis(discrete = TRUE) +
  guides(fill = FALSE) +
  labs(y="Code size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

ggsave(path(PLOT_DIR, "programs-code.pdf"), width=7, height=5.5)
```

```{r programs-runtime, eval=F}
programs %>%
  ggplot(aes(y=runtime, x=corpus, fill=corpus)) + 
  geom_flat_violin(trim=FALSE, width=.5) +
  geom_dotplot(
    binaxis="y", 
    dotsize=0.1, 
    stackdir="down", 
    binwidth=0.01, 
    position=position_nudge(-0.025)) +
  scale_y_log10(labels = function(x, ...) {
    min <- as.integer(x/60L)
    sec <- as.integer(x%%60L)
    sprintf("%.2d:%.2d", min, sec)
  }) +
  scale_x_discrete(labels=c("kaggle"="Kaggle", "packages"="Packages")) +
  scale_fill_viridis(discrete = TRUE) +
  guides(fill = FALSE) +
  labs(y="Running time [mm:ss] (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )
ggsave(path(PLOT_DIR, "programs-runtime.pdf"), width=3.5, height=5.0)
```

>>>>

---
title: "Usage metrics"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/
---

@@

source("inc/functions.R")
source("inc/latextags.R")
source("inc/paths.R")

create_tags(path(TAGS_DIR, "corpus.tex"), prefix = "", default = TRUE)
theme_set(theme_minimal())
```

@@

```{r load corpus}
CRAN_eval_traces <- 
  read_fst(PACKAGE_SUM_CALLS_FILE) %>%
  # remove evals that are inside the scripts,
  # for CRAN we are only interested in evals in packages
  filter(!str_starts(eval_call_srcref, "::global::main")) %>% 
  as_tibble()

CRAN_eval_traces_per_package <- 
  count(CRAN_eval_traces, caller_package, eval_call_srcref) %>%
  count(caller_package) %>% 
  rename(package=caller_package, evals_hit=n)

ALL_CRAN <- 
  read_fst(CORPUS_ALL_FILE) %>%
  mutate_if(is.numeric, replace_na, 0) %>%
  mutate(evals=as.integer(evals)) %>% 
  filter(loadable, package_code > 0) %>% 
  as_tibble()

CRAN <- 
  read_fst(CORPUS_FILE) %>%
  filter(package_code > 0) %>%
  left_join(CRAN_eval_traces_per_package, by="package") %>% 
  mutate_if(is.numeric, replace_na, 0) %>%
  mutate(
    evals=as.integer(evals),
    evals_hit=as.integer(evals_hit),
    # this is the case when there is eval in package loading code
    # this we will always run
    evals_hit=if_else(evals_hit > evals, evals, evals_hit),
    evals_coverage=evals_hit/evals
  ) %>% 
  as_tibble()

ALL_CRAN_eval_callsites <- 
  read_csv(PACKAGE_EVALS_STATIC_FILE) %>% 
  # TODO: There are very few NA, plus when srcref is NA, the rest of the row in NA
  # we should look at this
  filter(!is.na(srcref))

CRAN_eval_callsites <- semi_join(ALL_CRAN_eval_callsites, CRAN, by="package")

ALL_KAGGLE <- local({
  kernels <- read_csv(KAGGLE_KERNEL_FILE)
  evals <- read_csv(KAGGLE_EVALS_STATIC_FILE) %>% count(package) %>% rename(evals=n)
  left_join(kernels, evals, by="package") 
}) %>%
  mutate_if(is.numeric, replace_na, 0) %>% 
  mutate(evals=as.integer(evals)) %>% 
  as_tibble()

KAGGLE <- filter(ALL_KAGGLE, evals > 0)
```

## Overview

```{r}
cran_all_funs <- sum(ALL_CRAN$funs_public) + sum(ALL_CRAN$funs_private)
cran_funs <- sum(CRAN$funs_public) + sum(CRAN$funs_private)
cran_funs_with_eval <- sum(CRAN$funs_with_eval)
cran_code <- sum(CRAN$package_code)
cran_all_code <- sum(ALL_CRAN$package_code)
cran_evals <- CRAN$evals
cran_evals_hit <- CRAN$evals_hit

overview_table(
  r("CRAN all packages", ALL_CRAN),
  r("CRAN packages", CRAN),
  r("CRAN packages ratio", ratio(CRAN, ALL_CRAN)),
  r("CRAN all code", cran_all_code),
  r("CRAN all r code", sum(ALL_CRAN$package_r_code)),
  r("CRAN all native code", sum(ALL_CRAN$package_native_code)),
  r("CRAN code", cran_code),
  r("CRAN code ratio", ratio(cran_code, cran_all_code)),
  r("CRAN all funs", cran_all_funs),
  r("CRAN funs", cran_funs),
  r("CRAN funs with eval", cran_funs_with_eval),
  r("CRAN funs with eval ratio", ratio(cran_funs_with_eval, cran_funs)),
  r("CRAN all funs with eval ratio", ratio(cran_funs_with_eval, cran_all_funs)),
  r("CRAN eval call sites", sum(cran_evals)),
  r("CRAN hit eval call sites", sum(cran_evals_hit)),
  r("CRAN hit eval call sites avg ratio", percent(mean(cran_evals_hit/cran_evals))),
  r("CRAN runnable scripts", sum(ALL_CRAN$runnable_files)),
  r("CRAN runnable code", sum(ALL_CRAN$runnable_code)),
  r("CRAN runnable code examples", sum(ALL_CRAN$runnable_code_examples)),
  r("CRAN runnable code tests", sum(ALL_CRAN$runnable_code_tests)),
  r("CRAN runnable code vignettes", sum(ALL_CRAN$runnable_code_vignettes)),
)
```

### Kaggle

```{r}
```

```{r}
kaggle <- distinct(ALL_KAGGLE, hash, .keep_all=TRUE)
kaggle_code <- sum(kaggle$code)
kaggle_evals <- filter(kaggle, evals > 0)
kaggle_evals_code <- sum(kaggle_evals$code)

overview_table(
  r("Kaggle kernels", ALL_KAGGLE),
  r("Kaggle duplicates", nrow(ALL_KAGGLE)-nrow(kaggle)),
  r("Kaggle unique", kaggle),
  r("Kaggle code", kaggle_code),
  r("Kaggle competitions", count(kaggle, competition)),
  r("Kaggle with evals", kaggle_evals),
  r("Kaggle with evals code", ratio(kaggle_evals_code, kaggle_code))
)
```

### Matching evals

```{r}
matched_eval_callsites <-
  left_join(
    CRAN_eval_callsites, 
    count(CRAN_eval_traces, eval_call_srcref), 
    by=c("srcref"="eval_call_srcref")
  ) %>%
  mutate(
    n=replace_na(n, 0)
  ) %>%
  rename(hit=n)
```

The dynamic analysis traced `r fmt(ratio(filter(matched_eval_callsites, hit>0), matched_eval_callsites))`

@@

```{r}
eval_call_sites_hist <- function(df, df_all, y_lab, max_evals=15L) {
  df %>% 
    mutate(
      evals=if_else(evals < max_evals, evals, max_evals)
    ) %>%
    ggplot(aes(x=evals)) + 
    geom_histogram(binwidth=1, color="black", fill="blue", alpha=0.3) +
    geom_vline(aes(xintercept=mean(df$evals)), linetype="dashed", color="red", size=0.2) +
    scale_x_continuous(
      limits=c(0, max_evals + 1), 
      breaks=as.integer(seq(1, 15, length.out=4)), 
      labels=function(x) c(head(x, -1), str_c(tail(x, 1), "+"))
    ) +
    scale_y_continuous(
      labels=scales::comma_format(accuracy=1),
      sec.axis=sec_axis(
        trans=~./nrow(df_all), 
        labels=scales::percent_format(accuracy=.1), 
        name=y_lab)
    ) +
    labs(x = "Eval call sites", y=y_lab) +
    theme(text = element_text(size=17),
          panel.grid.minor.x = element_blank(), aspect.ratio = 4/3) 
}

eval_call_sites_hist(CRAN, ALL_CRAN, "CRAN packages")
#ggsave(path(PLOT_DIR, "cran-eval-callsites-hist.pdf"))
eval_call_sites_hist(KAGGLE, ALL_KAGGLE, "KAGGLE programs")
#ggsave(path(PLOT_DIR, "kaggle-eval-callsites-hist.pdf"))
```

### 2021-01-01 paper/main.tex
Polish usage metrics
Add 3.1

Our corpus is assembled out of two set of programs, one consisting of
popular libraries obtained from the Comprehensive R Archive
Network\footnote{CRAN is the largest repository of R code with over
\CorpusAllCranRnd packages. It receives about 6 new package
submissions a day~\cite{Ligges2017}. Unlike other open code
repositories such as GitHub, CRAN is a curated repository. Each
submitted package must abide to a number of well-formedness rules that
are automatically checked asserting certain quality. Most relevant for
this work is that all of the runnable code is tested and only a
successfully running package is admitted in the archive.} (we refer to
it as {\bf CRAN}) and the other from the Kaggle data science
competition (written {\bf Kaggle}). The intent here is to contrast
code written by experienced developpers (CRAN) with code authored by
typical end users of the language (Kaggle).

All the code in our is runnable, i.e. we have scripts that invoke the
CRAN packages and the Kaggle programs have input data. Clearly code
coverage will vary; as is the case for any dynamic analysis, the
quality of results is predicated on how representative the executions
we can observe are with respect to all possible runs of the corpus. To
mitigate the threat to validity attached to limited coverage, we
obtain clients that will generate multiple \emph{runs} of CRAN
packages. In this context, a run is the execution of a CRAN package or
Kaggle program with a particular set of input values.

\mypara{CRAN Packages.} The packages that are included
in this study are the top \CorpusPackages packages based on their
reverse dependencies. The set of reverse dependencies for some package
\emph{P} is transitive closure of packages that import \emph{P}. The
hypothesis underlying that choice is that packages with a large set of
reverse depencies are likely to be higher in quality and their tests
will provide better coverage. The packages are implemented in R with
some C and Fortran code. Using \c{cloc}, we measure a total
\CorpusRCodeRnd lines of R code and \CorpusNativeCodeRnd lines of
native code. For each package, we use its runnable code (tests, etc.)
to compute code coverage. On average, the cde coverage is
\CorpusMeanExprCoverage which is acceptable without being exhaustive.
Figure~\ref{fig:corpus} shows these packages, the size of the dots
reflects the project's size in lines of code. The x-axis indicates
code coverage in percents and the y-axis gives the number of call
sites to \eval that were traced, in log scale. Dotted lines indicate
means. Packages with over \CorpusEvalsPackageTreshold eval call sites
are named.

\begin{figure}[!h]\centering\includegraphics[width=.7\linewidth]
  {corpus.pdf}\caption{CRAN packages}\label{fig:corpus}
\end{figure}

To analyze a package, we need client code that invokes its methods.
There are three sources of built-in runnable code that come with each
CRAN package: \emph{tests, examples} and \emph{vignettes}. They are,
respectively, traditional unit tests, code snippets from the
documentation, and long-form use-cases written in Rmarkdown. Examples
and vignettes are automatically extracted and turned into scripts,
their input is bundled with the package. Most tests had to be discared
due to a limitation of our pipeline: the \c{testthat} harness uses
\eval and thus causes the entire test to register as an \eval call.
The selected packages are bundled with \CorpusPackagePrograms
programs; \CorpusExamplesProgramsRnd examples and
\CorpusVignettesProgramsRnd vignettes.

\mypara{Kaggle Scripts.} Kaggle is an online platform
for data-science and machine-learning. The website allows people to
submit data-analysis problems, users compete to find the best
solution. The solutions are uploaded to the platform as either plain
scripts or notebooks. We chose one of the most popular competition,
predicting the survival of passengers the
Titanic\footnote{\url{https://www.kaggle.com/c/titanic}}. Unlike CRAN,
Kaggle is not curated. After downloading the \CorpusKaggle solutions
and extracting the R code, we found that \CorpusDuplicatedKaggle were
duplicates. From the remaining \CorpusRunnableKaggle solutions,
\CorpusFailedKaggle failed to execute. Next to various runtime
exceptions, common problems were parse errors and misspelled package
names. The final set contains \CorpusFinishedKaggle programs
implemented in \CorpusFinishedKaggleCodeRnd lines of R code.

@@

\begin{figure}[h!]
 \includegraphics[width=1.061\textwidth]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{figure}

@@

\begin{figure}[h!]
\begin{tabular}{@{}c@{}c@{}}
\begin{minipage}{7.5cm}
 \includegraphics[width=\textwidth]{events_per_pack_small}
\end{minipage}&\begin{minipage}{7.5cm}
  \includegraphics[width=\textwidth]{events_per_pack_large}
\end{minipage}\\[-3mm]
\small (a) Small & \small (b) Large
\end{tabular}
 \caption{Events per packages} \label{ev}
\end{figure}

@@

\begin{itemize}
\item Figure 5(b) -- make `count` and `average` smaller.
\item Figure 6: (1) Replace `ast-nodes` with `nodes`
\item Figure 6: (2) Remove gray lines
\item Figure 6: increase font size
\item Figure 6: Try to make the figure less wide. Thinner bars/aspect
  ratio change.
\item Figure 7: check that element counts are correct
\item Figure 7: replace events by instructions. Check what we are
  counting? Are these bytecodes or AST nodes.
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\item I am having second thoughts about keeping the \c{ggplot2} data
  -- it is a big outlier that skews all the graphs...
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\item Add paragraphs for Kaggle and CORE -- only discuss the
  differences from CRAN
\end{itemize}

>>>>

Our corpus is assembled out of two set of programs, one consisting of libraries
obtained from \emph{CRAN} (Comprehensive R Archive Network\footnote{CRAN is the
  largest repository of R code with over \CorpusAllCranRnd packages. It receives
  about 6 new package submissions a day~\cite{Ligges2017}}) and the other from
the \emph{Kaggle} data science competition website\footnote{\cf
  \url{https://kaggle.com}}. The intent here is to contrast code written by
experienced developers (CRAN) with code authored by typical end users of the
language (Kaggle). Another difference is that CRAN is a curated repository. Each
submitted package must abide to a number of well-formedness rules that are
automatically checked asserting certain quality. Most relevant for this work is
that all of the runnable code is tested and only a successfully running package
is admitted in the archive. Kaggle on the other hand is more like GitHub, anyone
can submit any code. All the code in our corpus is runnable, \ie we have scripts
that invoke the CRAN packages and the Kaggle programs have input data.

% Clearly code coverage will vary; as is the case for any dynamic analysis, the
% quality of results is predicated on how representative the executions we can
% observe are with respect to all possible runs of the corpus. To mitigate the
% threat to validity attached to limited coverage, we obtain clients that will
% generate multiple \emph{runs} of CRAN packages. In this context, a run is the
% execution of a CRAN package or Kaggle program with a particular set of input
% values.

% \begin{figure}[!h]\centering\includegraphics[width=.7\linewidth]
%   {corpus.pdf}\caption{CRAN packages}\label{fig:corpus}
% \end{figure}

\mypara{CRAN Packages.} We used \CranAllPackages packages. These are almost all
of the available packages except for a few that we could not install due to
missing native dependencies. The packages are implemented in R with native C and
Fortran code. Using \c{cloc}, we measure a total \CranAllRCodeRnd lines of R
code and \CranAllNativeCodeRnd lines of native code. Out of these packages,
\CranPackages (\CranPackagesRatio) call eval. These packages represent
\CranCodeRatio of the code size.

To analyze a package, we need client code that invokes its methods. There are
three sources of built-in runnable code that come with each CRAN package:
\emph{tests, examples} and \emph{vignettes}. They are, respectively, traditional
unit tests, code snippets from the documentation, and long-form use-cases
written in \LaTeX\xspace or Markdown with executable snippets of R code.
Examples and vignettes are automatically extracted and turned into scripts,
their input is bundled with the package. Tests are directly runnable. Together
we there are \CranRunnableScripts scripts that contain \CranRunnableCode lines
of code (\CranRunnableCodeExamplesRnd in examples, \CranRunnableCodeVignettesRnd
in vignettes and \CranRunnableCodeTestsRnd in tests).

\mypara{Kaggle Scripts.} Kaggle is an online platform for data-science and
machine-learning. The website allows people to submit data-analysis problems,
users compete to find the best solution. The solutions, called \emph{kernels},
are uploaded to the platform as either plain scripts or notebooks. We obtained
\KaggleKernels kernels. Since Kaggle is not a curated repository, we first had
to remove duplicates. We used SHA-1 hash to identify \KaggleDuplicates
whole-file copies. The remaining \KaggleUnique kernels represent unique
solutions to \KaggleCompetitions Kaggle competition. Together, they contain
\KaggleCode lines of R code. Out of the \KaggleUniqueRnd kernels, only
\KaggleWithEvals contain calls to eval.

@@

\begin{figure}[h!]
 \includegraphics[width=0.5\textwidth, trim=5.5cm 0 6cm 0, clip]{size_loaded_distribution}
\caption{Loaded code} \label{fig:sizedistribution}
\end{figure}

@@

\begin{figure}[h!]
\begin{tabular}{@{}c@{}c@{}}
\begin{minipage}{7.5cm}
 \includegraphics[width=\textwidth]{events_per_pack_small}
\end{minipage}&\begin{minipage}{7.5cm}
  \includegraphics[width=\textwidth]{events_per_pack_large}
\end{minipage}\\[-3mm]
\small (a) Small & \small (b) Large
\end{tabular}
 \caption{Instructions per packages} \label{ev}
\end{figure}

@@

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\item I am having second thoughts about keeping the \c{ggplot2} data
  -- it is a big outlier that skews all the graphs...
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\item Add paragraphs for Kaggle and CORE -- only discuss the
  differences from CRAN
\end{itemize}
